---
title: Descriptive Analyses of Google Review Data
subtitle: 
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    number_sections: false
    theme: cerulean
    toc_float: true
    code_folding: hide
---
  
******
******

```{r setup, include = F}
rm(list=ls())

# load packages
library(tidyverse) 
library(knitr)
library(rmarkdown)
library(broom)
library(langcog)
library(magrittr)
library(ggmap)
library(tidytext)
library(remoji)
library(feather)
library(stringr)
library(quanteda)
library(corrr)

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, tidy = F,  cache = F, fig.height = 4)
```  

```{r}
# params
CUTOFF <- 9 # numer of reviews cutoff
#STORE_TYPE <- "Casey's General Store"
STORE_TYPE <- "SUBWAY®Restaurants"
```
Read in all reviews and merge in metadata
```{r}
all.review.files <- list.files("../data/reviews/")

all.reviews = map(all.review.files, function(x) {
    read_feather(paste0("../data/reviews/", x)) %>%
    mutate(city = unlist(str_split(x, "_"))[1])}) %>%
  bind_rows() 

all.reviews.clean = all.reviews %>%
    filter(!is.na(reviews)) %>%
    filter(reviews != "") %>%
    select(city, place.id, reviews, author.names) %>%
    mutate_all(funs(as.factor))

all.place_id.files <- list.files("../data/place_ids/")
all.place_id.meta = map(all.place_id.files, function(x) {
    read_feather(paste0("../data/place_ids/", x))}) %>%
  bind_rows() %>%
  rename(city = location)

all.place_id.meta.clean = all.place_id.meta %>%
              select(place.id, city, types, name) %>%
              mutate_all(funs(as.factor)) %>%
              distinct(place.id, city, types, name) # some place ids are duplicated across cities
            
# merge on place id
d = left_join(all.reviews.clean, all.place_id.meta.clean) %>%
      mutate(review_num = 1:nrow(.)) %>%
      select(review_num, city, place.id, types, city, name, reviews, author.names) %>%
      filter(name == STORE_TYPE)
```

There are `r nrow(all.reviews.clean)` in total.

Distribution of store types
```{r, eval = F}
all.place_id.meta.clean %>%
  group_by(name, city) %>%
  slice(1)%>%
  group_by(name)%>%
  summarize(n = n()) %>%
  arrange(-n)

```

## Distribution of number of reviews by city
What does the distribution of cities look like across cities?
```{r}
n.place.per.city = d %>%
  group_by(city, name) %>%
  slice(1) %>%
  group_by(city) %>%
  summarize(n = n())

ggplot(n.place.per.city, aes(x = n)) +
  geom_histogram() +
  theme_bw() +
  ggtitle("# place with reviews per city")

# ggplot(n.place.per.city, aes(x = "", y = n)) +
#   geom_boxplot() +
#   theme_bw() +
#   ggtitle("# place with reviews per city") +
#   xlab("")

big.cities = n.place.per.city 
#  filter(n > CUTOFF) 
```

There are `r nrow(big.cities)` cities with at least `r CUTOFF + 1` reviews. 

### Geographical distribution
```{r}
big.cities = left_join(big.cities, 
                       all.place_id.meta %>% select(city, lat, lon) %>% 
                         group_by(city) %>% slice(1))

iowa_bounding_box = c(-96.6397171020508, 40.3755989074707, # southwest coordinates
                      -90.1400604248047, 43.5011367797852) # northeast coordinates

map <- get_stamenmap(iowa_bounding_box, zoom = 5, maptype = "toner-lite")

ggmap(map) +
  geom_point(aes(x = lon, y = lat, size = log(n)), 
             data = big.cities, alpha = .5, color = "red") +
  theme_bw()
```

Now we're only going to include these cities.
```{r}
d.big = d %>%
  filter(city %in% unique(big.cities$city))
```

## Linguistic Measures by City
We calculate these measure on each review and then get city mean. 

### Character measures (prop neg, q, cap, emoji)
```{r}
# reg expression for emojis
emj <- paste(unlist(trimws(emoji(list_emoji(), TRUE))), collapse = "|")

d.big = d.big %>%
  mutate(reviews.clean = trimws(str_replace_all(reviews," "," ")),# remove extra spaces
         reviews.clean = str_replace_all(reviews.clean, "http[[:alnum:]]*", ""), # remove urls  
         reviews.clean = str_replace_all(reviews.clean, "\n|\"", ""),
         reviews.clean = str_replace_all(reviews.clean, emj, "EMOJI"),
         reviews.clean = str_replace_all(reviews.clean, ":\\)|:\\(|:-\\)|:-\\(", "EMOJI")) # remove emjois

d.big = d.big %>%
  rowwise() %>%
  mutate(review.length = str_length(reviews.clean),
         prop.cap = length(unlist(regmatches(reviews.clean, gregexpr("[A-Z]", reviews.clean, perl=TRUE))))/review.length,
         prop.exclam =  sum(gregexpr("[!]", reviews.clean)[[1]] > 0)/review.length,
         prop.emoji = sum(gregexpr("EMOJI", reviews.clean)[[1]] > 0)/review.length)
```


### Distribution of linguistic measures by city
```{r}
long.d = d.big %>%
  select(city, review.length, prop.cap, prop.exclam, prop.emoji) %>%
  gather(measure, value, 2:5)

city.d = long.d %>%
  group_by(city, measure) %>%
  summarize(mean = mean(value, na.rm = T))

ggplot(city.d %>% filter(measure != "review.length"), aes(x = log(mean))) +
         facet_wrap(~measure, scales = "free") +
  geom_histogram(aes(fill = measure)) +
  theme_bw() +
  theme(legend.position = "none") 

ggplot(city.d %>% filter(measure == "review.length"), aes(x = log(mean))) +
         facet_wrap(~measure, scales = "free") +
  geom_histogram(aes(fill = measure)) +
  theme_bw() +
  theme(legend.position = "none") 
```

### Geographical distribution
```{r}
city.d.coord = inner_join(ungroup(city.d), 
            all.place_id.meta %>% select(city, lat, lon) %>% group_by(city) %>% slice(1))

ggmap(map) +
  geom_point(aes(x = lon, y = lat, alpha = log(mean)), 
             data = filter(city.d.coord, measure == "review.length"), 
             color = "red") +
  ggtitle("log length") +
  theme_bw()
```

```{r}

city.d.coord = city.d.coord %>%
  mutate(log.prop.cap = ifelse(measure == "prop.cap",log(mean), mean ))
is.na(city.d.coord)<-sapply(city.d.coord, is.infinite)

ggmap(map) +
  geom_point(aes(x = lon, y = lat, alpha = log.prop.cap), 
             data = filter(city.d.coord, measure == "prop.cap"), 
             color = "red") +
  ggtitle("log prop capitalization") +
  theme_bw()
```

```{r}
ggmap(map) +
  geom_point(aes(x = lon, y = lat, alpha = log(mean)), 
             data = filter(city.d.coord,
                           measure == "prop.exclam" & mean != 0) , 
             color = "red") +
  ggtitle("log prop exclam") +
  theme_bw()
```

```{r}
ggmap(map) +
  geom_point(aes(x = lon, y = lat, alpha = log(mean)), 
             data = filter(city.d.coord,
                           measure == "prop.emoji" & mean != 0) , 
             color = "red") +
  ggtitle("log prop emoji") +
  theme_bw()
```

## Corpus-wide measures (across city)
### Sentiment

Create corpus for each city

```{r}
d.tokenized <- d.big %>%
  ungroup() %>%
  mutate(reviews = as.character(reviews)) %>%
  unnest_tokens(word, reviews) 
# remove stop words
data(stop_words)

d.tokenized.clean <- d.tokenized %>%
  anti_join(stop_words)

counts = d.tokenized.clean %>%
  count(word, sort = TRUE) %>%
  arrange(n)
  
# remove infrequent words
infrequent.words = d.tokenized.clean %>%
  count(word, sort = TRUE) %>%
  filter(n < 10) 

d.tokenized.clean = d.tokenized.clean %>%
  anti_join(infrequent.words)

affin = d.tokenized.clean %>% 
  inner_join(get_sentiments("afinn")) %>%
  group_by(city) %>%
  summarize(mean = mean(score, na.rm = T)) %>%
  arrange(mean)

# num words per 
numwords = d.tokenized.clean %>%
  group_by(city) %>%
  summarize(n = n()) %>%
  arrange(n)
```

```{r, eval = F}
bingnegative <- get_sentiments("bing") %>% 
  filter(sentiment == "negative")

wordcounts <- d.tokenized %>%
  group_by(review_num) %>%
  summarize(num_words = n()) %>%
  select(city, review_num, word)

prop.negative = d.tokenized %>%
  semi_join(bingnegative) %>%
  group_by(review_num) %>%
  summarize(negativewords = n()) %>%
  left_join(wordcounts, by = "review_num") %>%
  mutate(prop.neg = negativewords/num_words) %>%
  ungroup() %>%
  select(review_num, prop.neg)
```


```{r}
affin = d.tokenized.clean %>% 
  inner_join(get_sentiments("afinn")) %>%
  group_by(city) %>%
  summarize(affin.mean = mean(score, na.rm = T)) %>%
  arrange(affin.mean)

affin.cord = inner_join(ungroup(affin), 
            all.place_id.meta %>% select(city, lat, lon) %>%
              group_by(city) %>% slice(1))

ggplot(affin.cord, aes(x = affin.mean)) +
  geom_histogram() +
  theme_bw() +
  ggtitle("Sentiment")
```

```{r}
ggmap(map) +
  geom_point(aes(x = lon, y = lat, alpha = affin.mean), 
             data = affin.cord, 
             color = "red") +
  ggtitle("Sentiment") +
  theme_bw()
```

### Lexical diversity
```{r}
city.corpus = d.tokenized.clean %>%
  group_by(city) %>%
  summarise(text=paste(word, collapse=" "))

docs =  corpus(city.corpus, 
               doc_id = "city", text_field = "text")

dfm_docs = dfm(docs, groups = "city")
unigram.diversity = textstat_lexdiv(dfm_docs, measure = "TTR") %>%
                    rownames_to_column() %>%
                    rename(city = rowname)
```

Sampling
```{r}
1:1000

num.words.per.city = d.tokenized.clean %>%
  group_by(city) %>%
  summarize(n = n()) %>%
  arrange(-n)

## mapy do walmart?

```

```{r}
unigram.diversity =   left_join(unigram.diversity, 
                                all.place_id.meta %>% select(city, lat, lon) %>% group_by(city) %>% slice(1))

ggmap(map) +
  geom_point(aes(x = lon, y = lat, alpha = TTR), 
             data = unigram.diversity, 
             color = "red") +
  ggtitle("TTR") +
  theme_bw()
```

### N-grams
```{r}
bigrams <- d.big %>%
  select(city, review_num, reviews) %>%
  group_by(city, reviews) %>%
  unnest_tokens(bigram, reviews, token = "ngrams", n = 2)

unigrams <- d.big %>%
  select(city, review_num, reviews) %>%
  ungroup() %>%
  mutate(reviews = as.character(reviews))%>%
  unnest_tokens(unigram, reviews)

num_unigrams = unigrams %>%
      ungroup() %>%
      group_by(city, unigram) %>%
      count(unigram, sort = TRUE) %>%
      group_by(city) %>%
      summarize(n.unigrams = n())

bigram.diversity = bigrams %>%
  group_by(city) %>%
  summarize(n.bigrams = n()) %>%
  left_join(num_unigrams, by = "city") %>%
  mutate(normalized.bigrams = n.bigrams/n.unigrams)

```

### All variables
```{r}
all.lang = city.d %>%
  spread(measure, mean) %>%
  left_join(unigram.diversity, by = "city") %>%
  left_join(bigram.diversity, by = "city") %>%  
  left_join(affin, by = "city") %>%
  mutate(log.review.length = log(review.length), 
         log.prop.cap = log(prop.cap), 
         log.prop.exclam = log(prop.exclam), 
         log.prop.emoji = log(prop.emoji)) %>%
  select(-review.length, -prop.cap, -prop.exclam,
         -prop.emoji, -U, -lgV0, -lgeV0)

is.na(all.lang)<-sapply(all.lang, is.infinite)
```


### Outcomes measures

Are linguistic measure correlated with outcomes measures
```{r}
dist = read_csv("../data/city_highway_distances.csv") %>%
  rename(city = location) %>%
  mutate(log.mindrive = log(mindrive),
         log.time = log(time)) %>%
  select(-mindrive, -mindist, -time)

all = all.lang %>%
  left_join(dist) %>%
  select(-lat, -lon) 

correlate(all[,-1]) %>%
  focus(TTR:log.time, mirror = TRUE) %>%
  shave(upper = TRUE) %>%
  rplot() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
cor.test(all$log.time, all$TTR)
```

```{r}


ggplot(all, aes(x = log.time, y = TTR)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_bw()

ggplot(all, aes(x = log.time, y = log.review.length)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_bw()


ggplot(all, aes(x = TTR, y = log.review.length)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_bw()

ggplot(all, aes(x = log.time, y = affin.mean)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_bw()

ggplot(all, aes(x = log.time, y = log.prop.emoji)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_bw()
```

Heteroscedasticity
##### TO DO : sample rows to get TTR; do subway# MTLD

http://www.vli-journal.org/issues/01.1/issue01.1.10.pdf
